A Graph-based Framework for Coverage Analysis in Autonomous Driving

### 2025-10-12 article/article.tex

@@

\begin{itemize}
    \item In autonomous driving, coverage analysis is a crucial step to ensure the safety and reliability of the system.
    \item In most situations, coverage arguments are collected either per coverage factor, or maybe up to 2 or 3 factor interactions.
    \item See for example \cite{foretellix2019} for an production grade implementation of state of the art coverage analysis.
    \item In contrast to existing approaches, this paper proposes a graph-based framework for coverage analysis.
    \item There are already other graph-based approaches for analysing and representing traffic scenes, see for example \cite{behr2021graph}.
    \item However, the work in that paper is not specifically focused on coverage analysis.
    \item Hence in this paper, graph based traffic scene representations are utilized for coverage analysis.
    \item This paper is structured as follows:
    \begin{itemize}
        \item In the first section, xxx
    \end{itemize}
\end{itemize}

\cite{wagner2022odd}

\cite{arzamasov2021data}

@@

\cite{berger2020survey}

@@

\cite{behr2021graph}

@@

\cite{bagheri2020ontology}

\cite{riedmaier2020realistic}

@@

\cite{pek2019generating}

>>>>

test2

@@

\begin{itemize}
    \item In autonomous driving, coverage analysis is a crucial step to ensure the safety and reliability of the system.
    \item In most situations, coverage arguments are collected either per coverage factor, or maybe up to 2 or 3 factor interactions.
    \item See for example \cite{foretellix2019} for an production grade implementation of state of the art coverage analysis.
    \item In contrast to existing approaches, this paper proposes a graph-based framework for coverage analysis.
    \item There are already other graph-based approaches for analysing and representing traffic scenes.
    \item However, the work in that paper is not specifically focused on coverage analysis.
    \item Hence in this paper, graph based traffic scene representations are utilized for coverage analysis.
    \item This paper is structured as follows:
    \begin{itemize}
        \item In the first section, xxx
    \end{itemize}
\end{itemize}

@@

@@

still to be added: https://sagroups.ieee.org/adwg/wp-content/uploads/sites/661/2024/10/ADWG_STV2_whitepaper.pdf

still to be added: https://www.vvm-projekt.de/securedl/sdl-eyJ0eXAiOiJKV1QiLCJhbGciOiJIUzI1NiJ9.eyJpYXQiOjE3NDc2OTIxNjgsImV4cCI6MTc0Nzc4MjE2OCwidXNlciI6MCwiZ3JvdXBzIjpbMCwtMV0sImZpbGUiOiJmaWxlYWRtaW4vdXNlcl91cGxvYWQvVlZNZXRob2Rlbl9adXNhbW1lbmZhc3NlbmRlcl9BYnNjaGx1c3NiZXJpY2h0X3YxLjBfenVyX1Zlc_f9d402f084002b57/VVMethoden_Zusammenfassender_Abschlussbericht_v1.0_zur_Veroeffentlichung.pdf

@@

\cite{bagschik2018ontologybasedscenecreation}

@@
